Use of asynchronous circuits and leakiness in modeling biological circuit of the Caulobacter Crescentus cell cycle

### 2017-02-15 asyncleakyn.tex
updated importance of sigmoidal and threshold intro

Many biological functions can be modeled with the Hill function, including mRNA production.  The sigmoidal shape of the Hill function is reminiscent of Voltage Transfer Characteristics of CMOS inverters.  As such, much of the design properties of CM
OS circuits can be carried over.    In an ODE model of the protein production and degradation with the Hill function, the steady state solutions are the Hill function divided by the degradation constant.  In general the equation is of the form: $\frac{dprotein}{dt}=g(inputs)-protein\cdot\lambda$  where the function $g()$ is a sigmoidal curve such as the Hill function and $\lambda$ is the degradation constant.  This sigmoidal curve is then an input (the proteins that initiate transcription and production of the protein) versus the output, the current concentration of the protein.  If we treat each protein as its own gate, there exists similar restorative properties of the protein gate.

@@

Thresholds are a concept used in engineering to divide a continuous region of signal into some discrete categories such as ‘0’ or ‘1’ for a binary system.  The basic requirement is that the thresholds must allow sustained propagation throughout a chain of components, that is a ‘0’ output from one component is read as a ‘0’ input to the next component and the information is retained during processing.  Usually there are a separate low and high threshold and an in between region in which the signal is undetermined. (ie. if the signal is below the low threshold then it is a 0 and if the signal is above the high threshold it is a 1)

>>>>

Many biological functions can be modeled with the Hill function, including mRNA production.  The sigmoidal shape of the Hill function is reminiscent of Voltage Transfer Characteristics of CMOS inverters.  As such, much of the design properties of CMOS circuits can be carried over.  The importance of the sigmoidal shape of the input vs output transfer curve during steady state allows for restoring property of the signal and hence unsullied propagation in its next stages.   In an ODE model of the protein production and degradation with the Hill function, the steady state solutions are the Hill function divided by the degradation constant.  In general the equation is of the form: $\frac{dprotein}{dt}=g(inputs)-protein\cdot\lambda$  where the function $g()$ is a sigmoidal curve such as the Hill function and $\lambda$ is the degradation constant.  This sigmoidal curve is then an input (the proteins that initiate transcription and production of the protein) versus the output, the current concentration of the protein.  If we treat each protein as its own gate, there exists similar restorative properties of the CMOS gate.

@@

The input and outputs of electronic devices similar to the chemical concentrations in a cell are actually continuous (analog).  The concept of a binary '1' or '0' is actually extracted from the original analog signal.  Thresholds allow the conversion of an analog signal into a binary signal.  Usually there is a low and a high threshold, and an in between region in which the signal is undetermined.(figure)  If the signal is below the low threshold then it is a binary '0' and if the signal is above the high threshold it is a binary '1'.  
